Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2018-01-15 paper-ieee-trans.tex
Added indigo-dc roles in Ansible Galaxy reference as footnote

Last but not least, as described in section \ref{sec:devops}, in order
to facilitate the usage of the INDIGO--DataCloud services, they can be deployed
automatically using either Ansible \cite{indigo-ansible} or Puppet
\cite{indigo-puppet} open--source configuration tools. The adoption of such Configuration Management
tools not only eases the consumption of the products developed by external users or
infrastructures, but also tackles the correct installation and configuration of the
services and applications. A representative example is the number of roles currently
hosted in the Ansible Galaxy portal for the project [ref].

>>>>

Last but not least, as described in section \ref{sec:devops}, in order
to facilitate the usage of the INDIGO--DataCloud services, they can be deployed
automatically using either Ansible \cite{indigo-ansible} or Puppet
\cite{indigo-puppet} open--source configuration tools. The adoption of such Configuration Management
tools not only eases the consumption of the products developed by external users or
infrastructures, but also tackles the correct installation and configuration of the
services and applications. A representative example is the \textit{50 roles} being 
developed within the project and currently hosted in the Ansible Galaxy portal for 
the project \footnote{https://galaxy.ansible.com/indigo-dc/}.
